% Project:  LaTeX Resume
% Author:   Sid Lacy

% Description: LaTeX resume template with an emphasis on relative simplicity
% Based largely off of github.com/jakegut/resume

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin = 0.25in]{geometry} % Margin width, minimum safe for printers AFAIK
\usepackage{charter} % Global text font
\usepackage{fontawesome} % Icons
\usepackage[hidelinks]{hyperref} % Allows for clean hyperlink content
\usepackage{titlesec} % Formatting for section headers
\usepackage{eqparbox} % Helps to align the Font Awesome icons

% Section header formatting
\titleformat{\section}{
    \vspace{-10pt}\large\scshape % Push section header up 5pt; display with size 'large'; format it in all caps
}{}{}{}[\titlerule\vspace{-5pt}] % Display line under section header for width of document; remove 5pt space below

% Aligns the Font Awesome icons; thanks to stackoverflow.com/questions/55502809
\newcommand{\alignicon}[2][nmbr]{\eqmakebox[#1]{\strut #2}}

% Starts top-level item formatting
% Accepts: {Title}{Institution}{Location}{Start Date}{End Date}
\newcommand{\topLevelItem}[4]{
    \textbf{#1}\hfill #4\newline
    \emph{#2\hfill #3}\newline
    \vspace{-18pt}\begin{itemize}
}

% Starts project-specific top-level item formatting
% Accepts: {Title}{Institution}{Location}{Start Date}{End Date}
\newcommand{\topLevelProjectItem}[2]{
    \textbf{#1}\hfill \emph{#2}\newline
    \vspace{-18pt}\begin{itemize}
}

% Ends top-level item formatting
\newcommand{\topLevelItemEnd}{\end{itemize}\vspace{5pt}}

% Low-level item formatting
% Accepts: {Description}
\newcommand{\lowLevelItem}[1]{
    \item\small{#1}\vspace{-8pt}
}

% Miscellaneous formatting
\renewcommand{\labelitemi}{$\rightarrow$} % Replaces list bullets with arrows

\begin{document}
    % Header
    \begin{center}
        % Info + icons beside name
        \noindent\alignicon\faEnvelope\quad\href{mailto:contact@swlacy.com}{contact@swlacy.com}\hfill % Email
        \href{https://linkedin.com/in/lacysw}{linkedin.com/in/lacysw}\quad\alignicon\faLinkedin\newline % LinkedIn profile
        \alignicon\faGlobe\quad\href{https://swlacy.com}{swlacy.com}\hfill % Website
        \href{https://github.com/lacysw}{github.com/lacysw}\quad\alignicon\faGithub\vspace*{-0.33in} % GitHub profile
        
         % Name
        {\fontsize{28}{0}\selectfont\scshape Sid Lacy}\vspace{5pt}
    \end{center}
    
    % Section 1: Experience
    \section*{Experience}
        % Element
        \topLevelItem{Security Engineer Intern (Incoming)}{Amazon Inc.}{Washington, D.C. Metro Area (Remote)}{June 2022 - Sept. 2022}
            \lowLevelItem{Incoming member of the Amazon Information Security Department in Washington, D.C.}
        \topLevelItemEnd
        % Element
        \topLevelItem{Computer Information Systems Department Tutor}{Whatcom Community College}{Bellingham, WA}{Oct. 2020 - Apr. 2022}
            \lowLevelItem{Teach and assist students with WCC Computer Information Systems Department coursework}
            \lowLevelItem{Technologies/objectives: Cisco CCNA prep, enterprise security fundamentals, Linux admin with Bash, OS architecture, OOP with Java}
        \topLevelItemEnd
        % Element
        \topLevelItem{IT Support Specialist (Short-Term Contract)}{Anvil Corporation}{Bellingham, WA}{Sept. 2021 — Oct. 2021}
            \lowLevelItem{Employed PowerShell and Quest KACE to automate network-based workstation re-imaging, improving deployment time metrics}
            \lowLevelItem{Performed hardware upgrades on workstations and servers to accelerate business-critical AutoCAD rendering processes}
            \lowLevelItem{Carried out on-site network maintenance and inventory cataloging to ensure consistant remote, WFH employee access}
        \topLevelItemEnd
        % Element
        \topLevelItem{Collegiate Cyber Defense Competition (Team Captain)}{Western Washington University}{Bellingham, WA}{Jan. 2021 — Mar. 2021; Jan. 2022 — Apr. 2022}
            \lowLevelItem{Managed the deployment and maintenance of Palo Alto Firewall + IPS to protect the network from external threats}
            \lowLevelItem{Hardened Windows and *nix systems and services; filed incident reports; prepared technical security documentation}
            \lowLevelItem{Provided organized and effective client support while under relentless attack by skilled industry professionals}
        \topLevelItemEnd
        
    % Section 2: Education
    \section*{Education}
        % Element
        \topLevelItem{Cybersecurity, BS}{Western Washington University (GPA: 3.93)}{Bellingham, WA}{Jan. 2021 — June 2023 (Expected)}
            \lowLevelItem{Relevant coursework: operating systems, databases, functional programming, computer architecture, technical writing, cyber law}
            \lowLevelItem{Academic experience with Java, C, Python, MySQL, Bash, PowerShell}
        \topLevelItemEnd
        % Element
        \topLevelItem{Political Science, BA}{Western Washington University (GPA: 3.93)}{Bellingham, WA}{Jan. 2021 — June 2023 (Expected)}
            \lowLevelItem{Relevant coursework: American legal structures}
        \topLevelItemEnd
        % Element
        \topLevelItem{Cybersecurity, AAS}{Whatcom Community College (GPA: 3.97; Graduated with Honors)}{Bellingham, WA}{Sept. 2017 — Dec. 2020}
            \lowLevelItem{Relevant coursework: Cisco CCNA Routing and Switching, network security architecture, implementing security policy, regulatory standards and compliance, firewall management, industrial control systems security, business/client service and professionalism}
            \lowLevelItem{Obtained WCC CIS Certificate of Network Administration}
            \lowLevelItem{Placement on Dean’s List for exemplary performance for ten consecutive academic quarters}
        \topLevelItemEnd
        
    % Section 3: Activities
    \section*{Activities}
        % Element
        \topLevelItem{WWU Cybersecurity Club}{Western Washington University}{Bellingham, WA}{Sept. 2020 — Present}
            \lowLevelItem{Club President and student event leader; Captain of the Western Washington University Cyber Defense Team}
            \lowLevelItem{Managed the complete redevelopment of club resources and organizational structure, increasing member count by over 10x in one year}
        \topLevelItemEnd
        % Element
        \topLevelItem{Department of Energy CyberForce Competition (Team Captain)}{Western Washington University}{Bellingham, WA}{Oct. 2021 — Nov. 2021}
            \lowLevelItem{Maintained professional client relations in a security management role against an assumed, actively exploited breach}
            \lowLevelItem{Prepared technical documentation, drafted reports to facilitate event organization}
        \topLevelItemEnd
        
    % Section 4: Projects
    \section*{Projects}
        % Element
        \topLevelProjectItem{Personal Website and Tech Blog}{\href{https://swlacy.com}{swlacy.com}}
            \lowLevelItem{Dedicated to educational technical articles related to competition/CTF reports, malware analysis, and security research}
            \lowLevelItem{Intermediate web development skills with HTML, JavaScript, CSS; Frameworks: React, Hugo}
            \lowLevelItem{Over 700 views per month}
        \topLevelItemEnd
        % Element
        \topLevelProjectItem{Discord Shell}{\href{https://github.com/lacysw/DiscordShell}{github.com/lacysw/DiscordShell}}
            \lowLevelItem{Discord API-powered botnet and C2 designed to infect Windows and Linux hosts while evading AV engines}
            \lowLevelItem{Built with Python, Bash, PowerShell; constructed for educational/demonstrative purposes}
        \topLevelItemEnd
        % Element
        \topLevelProjectItem{Home Lab}{\href{https://github.com/lacysw/DiscordShell}{\href{https://swlacy.com/netdiag}{swlacy.com/netdiag}}}
            \lowLevelItem{Proxmox VM cluster: self-hosted DNS with domain-filtering, isolated malware analysis lab, remote development environment, file storage system, media server appliances, CTF images, various game servers}
            \lowLevelItem{External access via WireGuard}
        \topLevelItemEnd
\end{document}
